---
title: "Paper flow dob latest"
author: "Gurudev Ilangovan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    df_print: tibble
    highlight: tango
    theme: flatly
    toc: yes
    toc_depth: 5
    toc_float: 
      collapsed: false
      smooth_scroll: true
    number_sections: true 
    code_folding: hide
---

```{r setup, results="hide"}
knitr::opts_chunk$set(cache = F, message = FALSE)
source("utils.R")
theme_set(theme_light())
```

# Error Generation

## Preprocessing


```{r preprocess}

# df_dob <- 
#   read_csv("data/paper2/raw/dob.csv", 
#              col_types = cols(voter_registration_number = "c")) %>% 
#   select(voter_reg_num = voter_registration_number, dob = bday, twin_dob = twin_bday, twin_id) %>% mutate(twin_id = ifelse(is.na(twin_dob), NA, twin_id))



(df_a <- 
    read_delim("mar17_ncvoter_all_1110.txt", delim = "\t") %>% 
    rename(name_suffix = name_suffix_lbl,
           mname = middle_name) %>% 
    mutate_if(is.character, str_squish))

  
(df_b <- 
    read_delim("mar25_ncvoter_all_1110.txt", delim = "\t") %>% 
    rename(name_suffix = name_suffix_lbl,birth_age = age_at_year_end,
           mname = middle_name) %>% 
    mutate_if(is.character, str_squish))
```
```{r preprocess}
df_bdays <- get_bdays(df_a, df_b, year_a = 2017, year_b = 2025)

write_csv(df_bdays, "dob_all_1110.csv")

```


```{r preprocess}

# df_dob <- 
#   read_csv("data/paper2/raw/dob.csv", 
#              col_types = cols(voter_registration_number = "c")) %>% 
#   select(voter_reg_num = voter_registration_number, dob = bday, twin_dob = twin_bday, twin_id) %>% mutate(twin_id = ifelse(is.na(twin_dob), NA, twin_id))

(df_dob <- 
  read_csv("dob_all_1110.csv"))

(df_a <- 
    read_delim("mar17_ncvoter_all_1110.txt", delim = "\t") %>% 
    rename(name_suffix = name_suffix_lbl,
           mname = middle_name) %>% 
    mutate_if(is.character, str_squish))

  
(df_b <- 
    read_delim("mar25_ncvoter_all_1110.txt", delim = "\t") %>% 
    rename(name_suffix = name_suffix_lbl,birth_age = age_at_year_end,
           mname = middle_name) %>% 
    mutate_if(is.character, str_squish))

df_error_dist <- read_csv("error_table.csv")

```

```{r,message=TRUE}
set.seed(37)
source("utils.R")
registerS3method("mess_data", "df_pairs", get("mess_data.df_pairs", envir = asNamespace("rlErrorGeneratoR")))

library(rlErrorGeneratoR)
source("married_name_change1.R")

# Step 1: Run generate_error per error_percent and save intermediate results

df_messed_collection <- tibble(error_percent = seq(0, 0.6, 0.05)) %>% 
  mutate(ls_egen = map(error_percent, function(e){
    message(glue("\n\n--> Generating errors for error_percent = {e}"))
    generate_error(df_a, df_b, df_dob, df_error_dist, e, err_mult = 1, err_mult_inc = 0.01)
  }))

# Save intermediate results
saveRDS(df_messed_collection, "df_messed_collection_ls_egen_only1110.rds")
message("✅ Step 1 complete: df_messed_collection saved to df_messed_collection_ls_egen_only1110.rds")


```
```{r,message=TRUE}
# Step 2: Load intermediate results
#df_messed_collection <- readRDS("df_messed_collection_ls_egen_only3.rds")

# Extract df_a_mod / df_b_mod
df_messed_collection <- df_messed_collection %>%
  mutate(df_a_mod = map(ls_egen, "df_a_mod"),
         df_b_mod = map(ls_egen, "df_b_mod"),
         df_error_record = map(ls_egen, "df_error_record"),
         err_mult = map_dbl(ls_egen, "err_mult"),
         percent_error_ids = map_dbl(ls_egen, "percent_error_ids"),
         percent_errors = map_dbl(ls_egen, "percent_errors"))

saveRDS(df_messed_collection, "df_messed_collection_step3_1105.rds")
message("✅ Step 2a complete: columns extracted, saved to df_messed_collection_step3_1110.rds")





```
```{r,message=TRUE}

source("utils.R")
registerS3method("mess_data", "df_pairs", get("mess_data.df_pairs", envir = asNamespace("rlErrorGeneratoR")))

library(rlErrorGeneratoR)
# Step 2b: Run generate_pairs separately → you can debug this step safely
#df_messed_collection <- readRDS("df_messed_collection_step3_2.rds")

df_messed_collection <- df_messed_collection %>%
  mutate(df_pairs = pmap(list(a = df_a_mod, b = df_b_mod, e = error_percent), function(a, b, e){
    message(glue("--> Generating df_pairs for error_percent = {e}"))
    generate_pairs(a, b, glue("percent_{e*100}"))  # Use your modified generate_pairs with block limit!
  }),
  size = map_int(df_pairs, ~ if (is.null(.x)) 0 else nrow(.x)))

saveRDS(df_messed_collection, "df_messed_collection_step4_complete1110.rds")
message("✅ Step 2b complete: df_pairs generated and saved to df_messed_collection_step4_complete1110.rds")



```


```{r read df_feature_collection, message=TRUE}
library(tidyverse)
library(glue)
library(progress)
source("utils.R")

dir.create("features_all1110", showWarnings = FALSE)

pb <- progress_bar$new(
  format = "⏳ [:bar] :current/:total :percent eta: :eta",
  total = nrow(df_messed_collection), clear = FALSE, width = 60
)

for (i in seq_len(nrow(df_messed_collection))) {
  row_i <- df_messed_collection[i, ]
  error_pct <- row_i$error_percent[[1]]
  message(glue("🔄 Processing row {i} (error_percent = {error_pct})"))

  df_feature_i <- NULL  # 

  tryCatch({
    df_feature_i <- add_feature_vector(
      df = row_i$df_pairs[[1]],
      df_a_mod = row_i$df_a_mod[[1]],
      df_b_mod = row_i$df_b_mod[[1]]
    )

    row_i$df_feature <- list(df_feature_i)
    row_i$size <- nrow(df_feature_i)

    rds_path <- glue("features_all1110/row_{i}.rds")
    write_rds(row_i, rds_path)
    message(glue("✅ Saved: {rds_path} ({nrow(df_feature_i)} rows)"))

  }, error = function(e) {
    message(glue("❌ Error in row {i}: {e$message} — Skipped."))
  })

  pb$tick()
  rm(row_i, df_feature_i)
  gc()
}
df_messed_collection_full <- list.files("features_all1110", pattern = "row_\\d+\\.rds", full.names = TRUE) %>%
  map_dfr(read_rds)

write_rds(df_messed_collection_full, "df_feature_collection_full1110.rds")




```

```{r}
df_messed_collection <- read_rds("df_feature_collection_full0122.rds")
```

```{r,message=TRUE}

source("utils.R")
library(dplyr)
library(purrr)
library(tidyr)

set.seed(133)

target_n <- 27000
test_size <- 17000

df_messed_collection <- 
  df_messed_collection_full %>%
  mutate(
    actual_n = map_int(df_feature, nrow),   
    sample_n = pmin(actual_n, target_n),    
    indices_all = map2(df_feature, sample_n, function(x, y) {
      sample(1:(nrow(x)), size = y)
    }),
    df_feature = map2(df_feature, indices_all, function(x, y) {
      x[y, ] %>% sample_n(length(y))  
    }),
    test_n = map_int(df_feature, nrow) %>% pmin(test_size), 
    df_test = map2(df_feature, test_n, function(x, y) {
      x[1:y, ]
    }),
    df_train_full = map2(df_feature, test_n, function(x, y) {
      if (nrow(x) > y) {
        x[(y + 1):nrow(x), ]
      } else {
        x[0, ]  
      }
    })
  ) %>%
  crossing(train_n = seq(1000, 10000, 3000)) %>% 
  mutate(
    df_train = map2(df_train_full, train_n, function(x, y) {
      if (nrow(x) >= y) {
        x[1:y, ]
      } else {
        x  
      }
    })
  ) %>%
  select(error_percent, train_n, df_train, df_test, everything())

df_messed_collection %>% write_rds("data/paper2/df_messed_collection1110.rds")




```


```{r}
df_messed_collection <- read_rds("data/paper2/df_messed_collection1110.rds")
```


```{r,message=TRUE}
library(dplyr)
library(purrr)
library(glue)

dir.create("data/paper2/split_models1725_1110", recursive = TRUE, showWarnings = FALSE)

df_messed_collection %>%
  select(error_percent, train_n, percent_errors, df_train, df_test) %>%
  pwalk(function(error_percent, train_n, percent_errors, df_train, df_test) {

    file_name <- glue("data/paper2/split_models1725_1110/model_e{error_percent}_n{train_n}.rds")

    model_data <- list(
      error_percent = error_percent,
      train_n = train_n,
      percent_errors = percent_errors,
      df_train = df_train,
      test_subsets = test_subsets
    )

    write_rds(model_data, file_name)
  })

```

```{r,message=TRUE}
library(dplyr)
library(purrr)
library(glue)

dir.create("data/paper2/split_models1725_1105", recursive = TRUE, showWarnings = FALSE)

df_messed_collection %>%
  select(error_percent, train_n, percent_errors, df_train, df_test) %>%
  pwalk(function(error_percent, train_n, percent_errors, df_train, df_test) {

    file_name <- glue("data/paper2/split_models1725_1105/model_e{error_percent}_n{train_n}.rds")

    model_data <- list(
      error_percent = error_percent,
      train_n = train_n,
      percent_errors = percent_errors,
      df_train = df_train,
      test_subsets = test_subsets
    )

    write_rds(model_data, file_name)
  })

```

```{r}
df_messed_collection <- read_rds("data/paper2/percent_0_df_matches_unexact.rds")
```





```{r}
set.seed(37)
source("utils.R")
registerS3method("mess_data", "df_pairs", get("mess_data.df_pairs", envir = asNamespace("rlErrorGeneratoR")))

library(rlErrorGeneratoR)
source("married_name_change1.R")

df_messed_collection <- 
  tibble(error_percent = seq(0, 0.6, 0.05)) %>% 
  print() %>% 
  mutate(
    ls_egen = map(error_percent, function(e){
      message(glue("\n\nerror percent target: {e}"))
      generate_error(df_a, 
                     df_b, 
                     df_dob, 
                     df_error_dist, 
                     e, 
                     err_mult = 1,
                     err_mult_inc = 0.01)
    })
  ) %>% 
  print() %>% 
  mutate(df_a_mod = map(ls_egen, "df_a_mod"),
         df_b_mod = map(ls_egen, "df_b_mod"),
         df_error_record = map(ls_egen, "df_error_record"),
         err_mult = map_dbl(ls_egen, "err_mult"),
         percent_error_ids = map_dbl(ls_egen, "percent_error_ids"),
         percent_errors = map_dbl(ls_egen, "percent_errors")) %>% 
  print() %>% 
  mutate(
         df_pairs = pmap(list(a = df_a_mod, 
                              b = df_b_mod, 
                              e = error_percent), function(a, b, e){
           generate_pairs(a, b, data_pref = glue("percent_{e*100}"))
         }),
         size = map_int(df_pairs, nrow)) %>% 
  print()


```

```{r}
df_messed_collection <- read_rds("data/paper2/percent_0_df_matches_unexact.rds")
```


```{r}
df_messed_collection <- read_rds("step1_error_percent.rds")

progressr::with_progress({
  p <- progressr::progressor(steps = nrow(df_messed_collection))
  
  df_messed_collection <- df_messed_collection %>%
    mutate(
      ls_egen = map(error_percent, function(e){
        message(glue("\n\nerror percent target: {e}"))
        result <- generate_error(df_a, df_b, df_dob, df_error_dist, e, err_mult = 1, err_mult_inc = 0.01)
        p(message = glue("Finished error_percent = {e}"))
        result
      })
    )
})

write_rds(df_messed_collection, "step2_with_ls_egen.rds")

```




df_messed_collection_1 <- tibble(error_percent = seq(0, 0.6, 0.05)) %>% 
  mutate(
    ls_egen = map(error_percent, function(e){
      message(glue("\n\nerror percent target: {e}"))
      generate_error(df_a, 
                     df_b, 
                     df_dob, 
                     df_error_dist, 
                     e, 
                     err_mult = 1,
                     err_mult_inc = 0.01)
    })
  )

saveRDS(df_messed_collection_1, "df_messed_collection_1.rds")
```






df_messed_collection <- 
  tibble(error_percent = seq(0, 0.6, 0.05)) %>% 
  print() %>% 
  mutate(
    ls_egen = map(error_percent, function(e){
      message(glue("\n\nerror percent target: {e}"))
      generate_error(df_a, 
                     df_b, 
                     df_dob, 
                     df_error_dist, 
                     e, 
                     err_mult = 1,
                     err_mult_inc = 0.01)
    })
  ) %>% 
  print() %>% 
  mutate(df_a_mod = map(ls_egen, "df_a_mod"),
         df_b_mod = map(ls_egen, "df_b_mod"),
         df_error_record = map(ls_egen, "df_error_record"),
         err_mult = map_dbl(ls_egen, "err_mult"),
         percent_error_ids = map_dbl(ls_egen, "percent_error_ids"),
         percent_errors = map_dbl(ls_egen, "percent_errors")) %>% 
  print() %>% 
  mutate(
         df_pairs = pmap(list(a = df_a_mod, 
                              b = df_b_mod, 
                              e = error_percent), function(a, b, e){
           generate_pairs(a, b, data_pref = glue("percent_{e*100}"))
         }),
         size = map_int(df_pairs, nrow)) %>% 
  print()

```
```{r}
library(dplyr)
library(tidyr)
library(purrr)

df_match_long <- df_messed_collection %>%
  filter(error_percent == 0) %>%   # 只保留 error_percent == 0 的行
  mutate(
    train_summary = map(df_train, ~ {
      .x %>%
        count(`match`) %>%
        mutate(source = "train", prop = round(100 * n / sum(n), 2))
    }),
    test_summary = map(df_test, ~ {
      .x %>%
        count(`match`) %>%
        mutate(source = "test", prop = round(100 * n / sum(n), 2))
    })
  ) %>%
  mutate(all_summary = map2(train_summary, test_summary, bind_rows)) %>%  # 合并 train/test
  select(error_percent, train_n, all_summary) %>%
  unnest(all_summary)

df_match_long

```

```{r}
library(dplyr)

df_match_long %>%
  filter(error_percent == 0, as.character(match) == "match") %>%  # 只保留 match
  group_by(source) %>%
  summarise(total_match = sum(n), .groups = "drop")

```

```{r read df_feature_collection, message=TRUE}
library(tidyverse)
library(glue)
library(progress)
source("utils.R")

dir.create("features_all", showWarnings = FALSE)

pb <- progress_bar$new(
  format = "⏳ [:bar] :current/:total :percent eta: :eta",
  total = nrow(df_messed_collection), clear = FALSE, width = 60
)

for (i in seq_len(nrow(df_messed_collection))) {
  row_i <- df_messed_collection[i, ]
  error_pct <- row_i$error_percent[[1]]
  message(glue("🔄 Processing row {i} (error_percent = {error_pct})"))

  df_feature_i <- NULL  # 

  tryCatch({
    df_feature_i <- add_feature_vector(
      df = row_i$df_pairs[[1]],
      df_a_mod = row_i$df_a_mod[[1]],
      df_b_mod = row_i$df_b_mod[[1]]
    )

    row_i$df_feature <- list(df_feature_i)
    row_i$size <- nrow(df_feature_i)

    rds_path <- glue("features_all/row_{i}.rds")
    write_rds(row_i, rds_path)
    message(glue("✅ Saved: {rds_path} ({nrow(df_feature_i)} rows)"))

  }, error = function(e) {
    message(glue("❌ Error in row {i}: {e$message} — Skipped."))
  })

  pb$tick()
  rm(row_i, df_feature_i)
  gc()
}
df_messed_collection_full <- list.files("features_all", pattern = "row_\\d+\\.rds", full.names = TRUE) %>%
  map_dfr(read_rds)

write_rds(df_messed_collection_full, "df_feature_collection_full.rds")




```

```
# Feature Engineering

Using a function called add_feature_vector to generate features. 



```{r}
df_messed_collection <-
  df_messed_collection %>% 
  # slice(13) %>% 
  mutate(df_feature = pmap(list(df_pair = df_pairs, 
                                df_a = df_a_mod,
                                df_b = df_b_mod), 
                           function(df_pair, df_a, df_b){
    # browser()
    message(glue("calculating feature vector for {nrow(df_pair)} records"))
    st <- Sys.time()
    df_res <- 
      df_pair %>%
      # sample_n(500) %>%
      add_feature_vector(df_a, df_b) %>%
      select(starts_with("metric"), match) %>%
      mutate(match = match %>% factor(levels = c("unmatch", "match"))) %>%
      as.data.frame()
    message(glue("{difftime(Sys.time(), st, units = 'mins')} minutes elapsed"))
    df_res
  }))
  
df_messed_collection <- 
  df_messed_collection %>% 
  mutate(size = df_feature %>% map_int(~(nrow(.))))

df_messed_collection$size

df_messed_collection %>%
  write_rds("df_feature_collection1.rds")
  
 df_messed_collection
```

```{r read df_feature_collection, echo=FALSE}
(df_messed_collection <- 
  read_rds("df_feature_collection.rds"))
```

One df_feature dataframe looks like these.
```{r view df_feature}
df_pairs_cleaned <- df_messed_collection$df_pairs[[7]] %>%
  select(-pair_id) %>%
  filter_na_rows()

df_a <- df_messed_collection$df_a_mod[[7]]
df_b <- df_messed_collection$df_b_mod[[7]]

add_feature_vector(df_pairs_cleaned, df_a, df_b)


df_messed_collection$df_feature[[7]] %>% 
  select(nzv(df_messed_collection$df_feature[[7]])) %>% 
  View()
```


# Modeling

## Modeling setup

```{r train_test_split}
sample_strat <- function(df, n = 200){
  match <- df$match
  row_num <- 1:nrow(df)
  
  m = ceiling(n/5)
  u = n - m
  
  indices_m = sample(row_num[match == "match"], m)
  indices_u = sample(row_num[match == "unmatch"], u)
  
  sample(c(indices_u, indices_m), n)
}

# df_all <- 
#   df_messed_collection$df_feature[[2]]

set.seed(23)
library(dplyr)
library(purrr)



df_messed_collection <- 
  df_messed_collection %>% 
  mutate(
    train_indices = map(df_feature, sample_strat, n = 31100),

    test_indices = map2(df_feature, train_indices, function(df, t) {
      setdiff(seq_len(nrow(df)), t)
    }),

    df_train = map2(df_feature, train_indices, function(df, t) {
      df[t, ]
    }),

    df_test = pmap(
      list(df_pairs, df_feature, test_indices),
      function(pairs, df, v) {
        df_combined <- bind_cols(pairs %>% select(-any_of("match")), df)

        df_combined$match <- factor(pairs$match, levels = c("unmatch", "match"))

        
        df_combined[v, ]
      }
    )
  )


train_control <- 
  trainControl(method = "cv", 
               number = 10,
               verboseIter = T,
               savePredictions = TRUE,
               classProbs = TRUE)
```


```{r}
  
df_messed_collection_mod <- 
  df_messed_collection %>% 
  # slice(2) %>%
  mutate(
    model_rf = pmap(list(e = error_percent,
                         df_tr = df_train,
                         df_ts = df_test),
                    function(e, df_tr, df_ts){
      message(glue("rf-{e}"))
      # browser()
      set.seed(3)
      model <-
        train(
            match ~ ., 
            data = df_tr,
            trControl = train_control,
            tuneGrid = expand.grid(.mtry = seq(3, 15, 2)),
            importance = TRUE,
            keep.forest= TRUE,
            preProcess = c("medianImpute"),
            ntree = 350,
            method = "rf",
            na.action = na.pass)
      print(model)
      print(caret::confusionMatrix(df_ts$match,
                                   predict(model, df_ts,
                                           na.action = na.pass),
                                   positive = "match"))
      model
    }),
    model_svm_radial = pmap(list(
                                 e = error_percent,
                                 df_tr = df_train,
                                 df_ts = df_test),
                            function(e, df_tr, df_ts){
      # browser()
      message(glue("svmRadial-{e}"))
      set.seed(13)
      model <-
        train(
            # x = df_tr[, -ncol(df_tr)],
            # y = df_tr[, "match"],
            match ~ ., 
            data = df_tr,
            trControl = train_control,
            preProcess = c("medianImpute"),
            method = "svmRadial",
            na.action = na.pass)
      print(model)
      print(caret::confusionMatrix(df_ts$match,
                                   predict(model,
                                           newdata = df_ts,
                                           na.action = na.pass),
                                   positive = "match"))
      model
    }),
    model_svm_linear = pmap(list(
                                 e = error_percent, 
                                 df_tr = df_train, 
                                 df_ts = df_test), 
                            function(e, df_tr, df_ts){
      message(glue("svmLinear-{e}"))
      # browser()
      set.seed(13)
      model <-
        train(
            # x = df_tr[, -ncol(df_tr)],
            # y = df_tr[, "match"],
            match ~ ., 
            data = df_tr,
            trControl = train_control,
            preProcess = c("medianImpute"),
            method = "svmLinear",
            na.action = na.pass)      
      print(model)
      print(caret::confusionMatrix(df_ts$match, 
                                   predict(model, df_ts, 
                                           na.action = na.pass),
                                   positive = "match"))
      model
    })
  )
  



df_messed_collection_mod %>% 
  write_rds("df_messed_collection_models.rds")
  
df_messed_collection
```

```{r}
  
df_messed_collection_mod <- 
  df_messed_collection %>% 
  mutate(
    # ✅ Random Forest
    model_rf = pmap(list(e = error_percent,
                         df_tr = df_train,
                         df_ts = df_test),
                    function(e, df_tr, df_ts){
      message(glue("rf-{e}"))
      set.seed(3)
      model <- train(
        match ~ ., 
        data = df_tr,
        method = "rf",
        trControl = train_control,
        tuneGrid = expand.grid(.mtry = seq(3, 15, 2)),
        importance = TRUE,
        keep.forest = TRUE,
        preProcess = c("medianImpute"),
        ntree = 350,
        na.action = na.pass
      )
      print(model)
      print(caret::confusionMatrix(
        df_ts$match,
        predict(model, df_ts, na.action = na.pass),
        positive = "match"
      ))
      model
    }),

    # ✅ XGBoost
    model_xgb = pmap(list(e = error_percent,
                          df_tr = df_train,
                          df_ts = df_test),
                     function(e, df_tr, df_ts){
      message(glue("xgbTree-{e}"))
      set.seed(7)
      model <- train(
        match ~ ., 
        data = df_tr,
        method = "xgbTree",
        trControl = train_control,
        preProcess = c("medianImpute"),
        tuneLength = 5,
        na.action = na.pass
      )
      print(model)
      print(caret::confusionMatrix(
        df_ts$match,
        predict(model, df_ts, na.action = na.pass),
        positive = "match"
      ))
      model
    }),

    # ✅ GLMNet (Elastic Net)
    model_glmnet = pmap(list(e = error_percent,
                             df_tr = df_train,
                             df_ts = df_test),
                        function(e, df_tr, df_ts){
      message(glue("glmnet-{e}"))
      set.seed(9)
      model <- train(
        match ~ .,
        data = df_tr,
        method = "glmnet",
        trControl = train_control,
        preProcess = c("medianImpute", "center", "scale"),
        tuneLength = 5,
        na.action = na.pass
      )
      print(model)
      print(caret::confusionMatrix(
        df_ts$match,
        predict(model, df_ts, na.action = na.pass),
        positive = "match"
      ))
      model
    })
  )

df_messed_collection_mod %>% 
  write_rds("df_messed_collection_models11.rds")

```



```{r read_models,echo=FALSE}
(df_messed_collection_mod <- 
  read_rds("df_messed_collection_models.rds"))

df_messed_collection_mod <- 
  df_messed_collection_mod %>% 
  gather(model, model_obj, starts_with("model")) %>% 
  select(model, everything()) %>% 
  mutate(model = model %>% str_replace("model_", ""))
```


```{r test_set_evaluation}
df_messed_collection <- 
  df_messed_collection_mod %>%
  rename(error_rate = error_percent) %>% 
  mutate(
    results = map2(model_obj, df_test, function(model, df){
      df %>%
      mutate(pair_id = 1:nrow(.)) %>%
      evaluate_model(model, df_test = .)
    }),
    metrics = map(results, ~.x$metrics$df_metric_table),
    confusion_matrix = map(results, ~.x$metrics$confusion_matrix),
    roc_curve = map(results, ~.x$metrics$roc_curve),
    pred_confidence = map(results, ~.x$confidence),
    error_rate =
           error_rate %>%
           as.character() %>%
           fct_inorder()
  )
```

df_model_metrics <-
  df_messed_collection %>%
  select(model, error_rate, metrics) %>%
  unnest(metrics) %>% 
  mutate(error_rate =
           error_rate %>% 
           as.character() %>% 
           fct_inorder())

df_model_metrics %>% 
  spread(error_rate, value) %>% 
  filter(metric %in% 
           c(c("accuracy", "precision", "recall", "f1","auc", "brier")))



plot_roc_all(df_messed_collection %>% 
              filter(model == "svm_radial"),
             model_col = error_rate)

# df_model_metrics %>%
#   filter(metric %in% 
#            c("accuracy", "precision", "recall", "f1","auc", "brier")) %>%
#   ggplot(aes(error_rate, value, group = model, col = model)) +
#   geom_line() +
#   geom_point() +
#   scale_y_continuous(breaks = seq(0, 1, 0.2), 
#                      limits = c(0, 1), 
#                      minor_breaks = NULL)+
#   facet_wrap(~metric) +
#   theme_light()

# df_model_metrics %>% 
#   filter(metric %in% c("accuracy", "precision", "recall", "f1","auc")) %>%
#   ggplot(aes(model, value, fill = model)) +
#   geom_col(position = "dodge") +
#   facet_grid(error_rate~metric) +
#   coord_flip()

df_model_metrics %>% filter(model == "rf", error_rate == 0.6)

#line plots
df_model_metrics %>% 
  filter(metric %in% c("f1", "precision", "recall")) %>% 
  ggplot(aes(error_rate, value, fill = model, col = model, group = model)) +
  geom_path() +
  geom_point() +
  scale_y_continuous(limits = c(0.8,1)) +
  facet_wrap(~metric, ncol = 1) +
  labs(x = "Error rate",
       y = "value") +
  scale_color_tableau()

ggsave("rateVf1.png", 
       dpi = 100, height = 15, width = 10, units = "in")


df_model_metrics %>% 
  filter(metric == "brier") %>% 
  ggplot(aes(error_rate, value, fill = model, col = model, group = model)) +
  geom_path() +
  geom_point() +
  scale_y_continuous(limits = c(0,0.04)) +
  labs(x = "Error rate",
       y = "Brier score") +
  scale_color_tableau()

ggsave("rateVbrier.png", 
       dpi = 100, height = 8, width = 8, units = "in")

#bar plots
df_model_metrics %>% 
  filter(metric == "brier") %>% 
  ggplot(aes(error_rate, value, fill = model)) +
  geom_col(position = "dodge")

df_confs <- 
  df_messed_collection %>% 
  mutate(conf = map(results, function(x){
    x$data$df_preds_aug %>% select(-match1)
  })) %>% 
  select(model, error_rate, conf) %>% 
  unnest() %>% 
  mutate(
    match_pred = match_pred %>% fct_rev(),
    grade = (match_pred == match) %>% as.integer(),
    brier = (ifelse(match == "match", 1, 0) - match_prob)^2
    )


         

calc_review_percent <- function(df_conf, value = 0.99){
  # browser()
  t <- 0.25
  df_thresh <- 
    df_conf %>% 
    filter(match_prob <= t | match_prob >= (1-t))
  
  while((F1_Score(df_thresh$match, 
                 df_thresh$match_pred, 
                 positive = "match") <= value) &
        (nrow(df_thresh) > 0)){
    if(t > 0.01){
      t <- t - 0.01
    } else {
      t <- t - 0.001
    }
    
    df_thresh <- 
      df_conf %>% 
      filter(match_prob <= t | match_prob >= (1-t))
  }
  
  n_review <- 
    df_conf %>% 
    anti_join(df_thresh, by = "pair_id") %>% 
    nrow(.)
  n_review_percent <- n_review/nrow(df_conf) 
  # print(n_review_percent)
  n_review_percent
}

df_review <- 
  df_confs %>% 
  group_by(error_rate, model) %>% 
  nest() %>% 
  # slice(15) %>%
  mutate(review_percent = 
           pmap_dbl(list(e = error_rate, m = model, d = data),
                    function(e, m, d){
                      message(glue("{m}-{e}"))
                      p <- calc_review_percent(d)
                      print(p)
                      p
                    }))

p <- 
  df_review %>% 
  ggplot(aes(error_rate, 
             review_percent, 
             # group = model, 
             # col = model,
             fill = model)) +
  geom_col(position = "dodge") +
  scale_fill_tableau()

ggplotly(p)

ggsave("rateVreview.png", 
       dpi = 100, height = 6, width = 10, units = "in")

df_confs %>% 
  filter(error_rate == 0.3, model == "svm_radial") %>% 
  calc_review_percent()

df_confs %>% 
  sample_n(nrow(.)) %>% 
  group_by(model, error_rate, match, match_pred) %>% 
  ggplot(aes(error_rate, match_prob, col = model, group = model)) +
  geom_jitter(height = 0, alpha = 0.1) +
  geom_smooth() +
  facet_grid(match ~ match_pred)

df_conf_sum <- 
  df_confs %>% 
  group_by(model, error_rate, match, match_pred) %>% 
  summarise(mean_prob = mean(match_prob),
            median_prob = median(match_prob))

df_conf_sum %>% 
  filter(error_rate == 0.3) %>% 
  group_by(model, match_pred) %>% 
  summarise(diff_prob = abs(first(mean_prob) - last(mean_prob)))
  
df_conf_sum %>% 
  ggplot(aes(error_rate, mean_prob, col = model, group = model)) +
  geom_line() +
  facet_grid(match ~ match_pred)
  

df_confs %>% 
  mutate(prob_review = match_prob %>% between(0.30, 0.70)) %>% 
  group_by(error_percent, model) %>% 
  summarise(review_percent = sum(prob_review)/n()) %>% 
  ggplot(aes(error_percent, review_percent, fill = model)) +
  geom_col(position = "dodge")

df_confs %>% 
  ggplot(aes(error_percent, match_prob)) +
  geom_boxplot() +
  facet_grid(grade~match_pred)

df_confs %>% 
  group_by(error_percent, model) %>% 
  summarise(brier = mean(brier)) %>%
  ggplot(aes(error_percent, brier, fill = model)) +
  geom_col(position = "dodge")

df_confs %>% 
  ggplot(aes(error_percent, brier)) +
  geom_jitter(height = 0, alpha = 0.5) +
  facet_wrap(~model)

df_model_metrics %>% 
  filter(metric == "accuracy") %>% 
  ggplot(aes())

```


## Size of labeled data 

```{r}
df_error_pl <- 
  df_messed_collection_mod %>% 
  mutate(error_rate =
           error_percent %>%
           as.character() %>%
           fct_inorder(),
         size_match =
           map_dbl(df_pairs,
                   function(df_pair){
                     mean(df_pair$match == "match")
                   }))
  
  
df_error_pl%>%
  filter(model == "rf") %>% 
  select(error_rate, df_pairs) %>% 
  unnest() %>% 
  mutate(match = match) %>%
  ggplot(aes(error_rate, fill = match)) +
  geom_bar() +
  theme_light() +
  scale_y_continuous(breaks = seq(0, 45000, 10000)) +
  scale_fill_tableau()

ggsave("rateVsize.png", dpi = 500, height = 8, width = 10)
```

```{r}
df_error_pl %>% 
  mutate(size = map_int(df_a_mod, nrow)) %>%
  select(error_rate, df_error_record, size) %>% 
  unnest() %>% 
  group_by(error_rate, size) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  add_row(error_rate = 0, size = nrow(df_error_pl$df_a_mod[[1]]), n = 0) %>% 
  arrange(error_rate) %>% 
  mutate(error_rate =
           error_rate %>%
           as.character() %>%
           fct_inorder(),
         prop = n/size) %>% 
  ggplot(aes(error_rate, n, group = 1)) +
  geom_path() +
  theme_light() +
  labs(
    x = "Error rate",
    y = "Number of errors introduced",
    subtitle = "Number of records ~ 16500"
  )

ggsave("/rateVraw_errors.png", 
       dpi = 100, height = 8, width = 8, units = "in")
p <- 
  df_error_pl %>% 
  select(error_rate, df_a_mod) %>% 
  unnest() %>% 
  select(error_rate, id_a) %>% 
  left_join(
    df_error_pl %>% 
    # mutate(size = map_int(df_a_mod, nrow)) %>%
    select(error_rate, df_error_record, size) %>% 
    unnest() %>% 
    group_by(error_rate) %>% 
    count(id) %>% 
    ungroup(),
    by = c("error_rate", "id_a" = "id")) %>% 
  mutate(num_errors_in_record = 
           ifelse(is.na(n), 0, n) %>% as.factor() %>% fct_rev()) %>% 
  ggplot(aes(error_rate, fill = num_errors_in_record)) +
  geom_bar(position = "fill") +
  # scale_fill_manual(values = lacroix_palette(5, type = "discrete")) +
  scale_fill_tableau(guide = guide_legend(
    title = 
    "Number of errors
    in a record"
  )) +
  theme_light() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Error rate", y = "Percent of records with n errors") +
  theme()# text = element_text(size = 20)

p

ggsave("/rateVerrors.png", width = 10, height = 8, dpi = 100)

ggplotly(p)
```

