```{r setup, results="hide"}
knitr::opts_chunk$set(cache = F, message = FALSE)
source("utils.R")
theme_set(theme_light())
```







```

```{r setup, results="hide"}
# ============================================================
# Libraries
# ============================================================
library(tidyverse)
library(caret)
library(glue)
library(pROC)
library(MLmetrics)
source("utils.R")  

# ============================================================
# Folder config
# ============================================================
input_folder <- "data/paper2/split_models1725_0122/"
output_folder <- "output1725/result0122"

file_list <- list.files(path = input_folder, pattern = "\\.rds$", full.names = TRUE)

# ============================================================
# Make sure output folder exists
# ============================================================
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)
}


# ============================================================
# Features to keep
# ============================================================
selected_features <- c(
  "pair_id", "match",
  "metric_fname_dl", "metric_fname_jw", "metric_fname_soundex",
  "metric_lname_dl", "metric_lname_jw", "metric_lname_soundex",
  "metric_name_swaps", "metric_ffreq_a", "metric_ffreq_b",
  "metric_lfreq_a", "metric_lfreq_b",
  "metric_dob_dist", "metric_year_dist", "metric_month_dist", "metric_day_dist",
  "metric_dm_swaps", "birth_year_a", "birth_year_b",
  "metric_gender_code_ff", "metric_gender_code_mm",
  "metric_race_code_same", "metric_race_code_ww_bb",
  "metric_potential_marriage"
)

# ============================================================
# Clean data function
# ============================================================
clean_data <- function(df_input) {
  df_input %>%
    select(all_of(selected_features)) %>%
    mutate(
      birth_year_a = as.numeric(birth_year_a),
      birth_year_b = as.numeric(birth_year_b),
      match = as.factor(match)   # ⭐ required for prSummary metrics
    )
}

# ============================================================
# Training across files
# ============================================================
for (file_path in file_list) {
  
  file_name <- tools::file_path_sans_ext(basename(file_path))
  message(glue("Processing file: {file_name}"))

  df <- read_rds(file_path)

  df_train <- clean_data(df$df_train)
  test_subsets <- map(df$test_subsets, clean_data)

  # ============================================================
  # STEP 1: Compute class weights
  # ============================================================
  pos_ratio <- mean(df_train$match == "1")
  neg_ratio <- mean(df_train$match == "0")

  # ⭐ Weight positive class more: focus on false positive penalty
  class_weights <- ifelse(
    df_train$match == "1",
    (neg_ratio / pos_ratio) * 1.8,  # <— BOOST precision
    1
  )

  # ============================================================
  # STEP 2: Configure prSummary
  # ============================================================
  # MUST HAVE classProbs + prSummary together
  train_control <- trainControl(
    method = "cv",
    number = 10,
    verboseIter = TRUE,
    savePredictions = TRUE,
    classProbs = TRUE,
    summaryFunction = prSummary   # ⭐ enable Precision/Recall/F1
  )

  # ============================================================
  # STEP 3: Train RF with F1 objective
  # ============================================================
  set.seed(230)

  model_rf <- train(
    match ~ . -pair_id,
    data = df_train,

    # ⭐ F1 optimization (caret calls F1 as "F")
    metric = "F",

    # ⭐ apply weights
    weights = class_weights,

    trControl = train_control,

    # wider search space to improve splitting behavior
    tuneGrid = expand.grid(.mtry = c(3,4,5,6,7,8)),

    method = "rf",
    ntree = 2000,
    na.action = na.pass,
    importance = TRUE,
    keep.forest = TRUE,
    preProcess = c("medianImpute")
  )

  # ============================================================
  # STEP 4: save trained RF
  # ============================================================
  saveRDS(model_rf, glue("{output_folder}/{file_name}_rf_trained.rds"))

  # ============================================================
  # STEP 5: Evaluate on test subsets
  # ============================================================
  rf_results_all <- tibble(
    subset = integer(),
    metrics = list(),
    confusion_matrix = list(),
    roc_curve = list(),
    pred_confidence = list()
  )

  for (i in seq_along(test_subsets)) {
    test_set <- test_subsets[[i]]
    message(glue("Evaluating on Test Subset {i}"))

    # this function should compute Precision, Recall, F1
    result <- evaluate_model(model_rf, df_test = test_set)

    rf_results_all <- bind_rows(
      rf_results_all,
      tibble(
        subset = i,
        metrics = list(result$metrics$df_metric_table),
        confusion_matrix = list(result$metrics$confusion_matrix),
        roc_curve = list(result$metrics$roc_curve),
        pred_confidence = list(result$confidence)
      )
    )
  }

  # ============================================================
  # Save full RF test results
  # ============================================================
  saveRDS(rf_results_all, glue("{output_folder}/{file_name}_rf_results_all.rds"))

  rf_metrics_long <- rf_results_all %>%
    mutate(metrics = map(metrics, ~ as_tibble(.x))) %>%
    unnest(metrics)

  write_csv(rf_metrics_long, glue("{output_folder}/{file_name}_rf_metrics_summary.csv"))

  message(glue("{file_name} processing completed."))
}

message("All files processed successfully.")

```



```{r,message=TRUE}

library(tidyverse)
library(caret)
library(glue)
library(pROC)
library(MLmetrics)
source("utils.R")  

input_folder <- "data/paper2/split_models1725_1105/"
output_folder <- "output1725/result0113"
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)
}
file_list <- list.files(path = input_folder, pattern = "\\.rds$", full.names = TRUE)

selected_features <- c(
  "pair_id", "match",
  "metric_fname_dl", "metric_fname_jw", "metric_fname_soundex",
  "metric_lname_dl", "metric_lname_jw", "metric_lname_soundex",
  "metric_name_swaps", "metric_ffreq_a", "metric_ffreq_b",
  "metric_lfreq_a", "metric_lfreq_b",
  "metric_dob_dist", "metric_year_dist", "metric_month_dist", "metric_day_dist",
  "metric_dm_swaps", "birth_year_a", "birth_year_b",
  "metric_gender_code_ff", "metric_gender_code_mm",
  "metric_race_code_same", "metric_race_code_ww_bb",
  "metric_potential_marriage"
)

clean_data <- function(df_input) {
  df_input %>%
    select(all_of(selected_features)) %>%
    mutate(
      birth_year_a = as.numeric(birth_year_a),
      birth_year_b = as.numeric(birth_year_b)
    )
}

for (file_path in file_list) {
  file_name <- tools::file_path_sans_ext(basename(file_path))
  message(glue("Processing file: {file_name}"))

  df <- read_rds(file_path)

  df_train <- clean_data(df$df_train)
  test_subsets <- map(df$test_subsets, clean_data)

  train_control <- trainControl(
    method = "cv",
    number = 5,
    verboseIter = TRUE,
    savePredictions = TRUE,
    classProbs = TRUE
  )

  set.seed(230)
  model_rf <- train(
    match ~ . -pair_id,
    data = df_train,
    trControl = train_control,
    tuneGrid = expand.grid(.mtry = c(2,3,4,5,6)),
    importance = TRUE,
    keep.forest = TRUE,
    metric = "Accuracy",
    preProcess = c("medianImpute"),
    ntree = 200,
    method = "rf",
    na.action = na.pass
  )

  saveRDS(model_rf, glue("{output_folder}/{file_name}_rf_trained.rds"))

  rf_results_all <- tibble(
    subset = integer(),
    metrics = list(),
    confusion_matrix = list(),
    roc_curve = list(),
    pred_confidence = list()
  )

  for (i in seq_along(test_subsets)) {
    test_set <- test_subsets[[i]]
    message(glue("Evaluating on Test Subset {i}"))

    result <- evaluate_model(model_rf, df_test = test_set)

    rf_results_all <- bind_rows(rf_results_all, tibble(
      subset = i,
      metrics = list(result$metrics$df_metric_table),
      confusion_matrix = list(result$metrics$confusion_matrix),
      roc_curve = list(result$metrics$roc_curve),
      pred_confidence = list(result$confidence)
    ))
  }

  saveRDS(rf_results_all, glue("{output_folder}/{file_name}_rf_results_all.rds"))

  rf_metrics_long <- rf_results_all %>%
    mutate(metrics = map(metrics, ~ as_tibble(.x))) %>%
    unnest(metrics)

  write_csv(rf_metrics_long, glue("{output_folder}/{file_name}_rf_metrics_summary.csv"))

  message(glue("{file_name} processing completed."))
}

message("All files processed successfully.")



```
